MSstatsPTM: Statistical relative quantification of post-translational modifications in bottom-up mass spectrometry-based proteomics

### 2022-07-29 main/MSstatsPTM_Main.tex
Small evaluations

We compared the performance of  $MSstatsPTM$ to that of \todo{ratio-based or both?} ANOVA and of Limma. Since IsobarPTM is only applicable to experiments with TMT labeling, it could not be applied to the datasets with known ground truth in this manuscript, and was excluded from the comparisons. \todo{ANOVA and Limma took as input protein summaries XXX}  $MSstatsPTM$ was used without imputing missing values, and without Empirical Bayes moderation. All the evaluations were done at the FDR-adjusted p-value cutoff of $q=.05$. More details are in {\bf Supplementary Sec. \ref{supp-sec:experiments}}.

>>>>

We compared the performance of  $MSstatsPTM$ to that of \todo{ratio-based or both?} ANOVA and of Limma. Since IsobarPTM is only applicable to experiments with TMT labeling, it could not be applied to the datasets with known ground truth in this manuscript, and was excluded from the comparisons. \todo{ANOVA and Limma took as input protein summaries XXX - define the variants of the same models (e.g., used in Fig 4)}  $MSstatsPTM$ was used without imputing missing values, and without Empirical Bayes moderation. All the evaluations were done at the FDR-adjusted p-value cutoff of $q=.05$. More details are in {\bf Supplementary Sec. \ref{supp-sec:experiments}}.
